---
title: "test"
---

```{r eval = TRUE,  message=F, include=FALSE, warning=F, purl=F, results="hide"}
knitr::purl('environment.Rmd', documentation = 0)
```


```{r echo=FALSE, purl=F}
xfun::embed_file('environment.Rmd')
```

```{r echo=FALSE, purl=F}
xfun::embed_file('environment.R')
```


```{r echo=FALSE, purl=F}
xfun::embed_file('C:/Users/user/Downloads/reef_fish.xlsx')
```

```{r echo=FALSE}
xaringanExtra::use_clipboard()
```

-----------------------
## Update

If you already have R on your computer, an alternative is to run the following line of code in R native GUI (<span style="color: red">it will tell you if your R version is out-of-date </span>): 

```{r,  eval=FALSE, tidy=TRUE}
# R update (to run in R native GUI only)
if(!require(installr)) {
  install.packages("installr"); require(installr)} 
updateR()
```

```

## Working directory

It is a good practice to create a working directory (folder) where you will store all your file. In general, each project will have its own working directory including data set, script, plot, etc. 

- retrieve your current working directory

```{r,  eval=F}
# get your current working directory
getwd()
```

You wanna change for a specific folder. Set it up using:

```{r,  eval=FALSE}
# set your current working directory
setwd()
```

## Calculator

R is a calculator:

```{r,  eval=FALSE}
# Use R as a calculator
3+2 # addition
3-2 # substraction
3*2 # multiplication
3/2 # division
3^3 # power
log(2) # logarithm
exp(2) # exponential
(5 + 3) / 4 # define priority using () or {} 
pi*4 # common function
```

R is case sensitive `pi` will work, whereas`Pi` will not 

## Objects

The list function `ls()` will provide you with all the objects in the memory.

```{r,  eval=T}
# Deleting all objects using rm()
rm(list = ls())
# my current list is empty 
ls()
```


```{r,  eval=T}
# I create and list 3 objects 
a<-'corals' # create an object 'a' containing 'corals'
b<-'are' # create an object 'b' containing 'are'
c<-'cool'# create an object 'c' containing 'cool'
ls() # list objects 'a', 'b', 'c'
```

**Note**: two operators `<-` and `=` can be used to import data. While longer, I favor `<-` in the creation of object to avoid confusion with mathematical operator

You can clean `rm` (remove) the objects `list`  in memory `ls()` using:

```{r,  eval=T}
# clean objects in memory
rm(list=ls())
```

**Tip**: The use of CTRL+L cleans your screen when you want to make it clearer. However, it **does not remove the objects** in memory.

## Reading

To be able to work with a dataset (and make calculation based on it), it has to be import as an object in the memory of R. Many formats can be used (.xls, .spss, SAS, etc.). To start with, we will use and .xlsx file, but quickly we will turn toward less 'heavy' format. Note the distinction between **reading** a file and **importing** a file.

My file `reef_fish` is an .xlsx file located in the file 'Data' of my working directory. 

```{r,  eval=T}
# 1. using the package `readxl`
# 2. reading my `reef_fish.xlsx` in my working directory
# 3. importing `reef_fish.xlsx` in a `fish` object
library(readxl) # load the package `readxl'
read_excel('C:/Users/user/Downloads/reef_fish.xlsx') # automatically print on my screen
fish<-read_excel('C:/Users/user/Downloads/reef_fish.xlsx') # store my table in an object called `fish`
fish # print my object `fish`   
```

More commonly, we will use .txt file (lighter) and the function `read.table'. But often you will need to think at several important **arguments** about the file you wanna to import:

- What is the exact name of the data file (with its extension)?
- Does the file have column titles?
- What is the delimiter between the columns (tabulation, space, comma or semicolon)?
- What is the character used for decimal points (dot, comma)?

```{r,  eval=T}
# importing a .txt file
fish<-read.table('C:/Users/user/Downloads/reef_fish.txt', header=T, sep='\t', dec='.') 
```

Check `?read.table` for all arguments you can specify within this function

It is not a good practice, but instead or working within  a working directory, you can also target directly your file (check your file properties) or an url.

```{r,  eval=FALSE,  tidy=TRUE}
# import file by path name
fish<-read.table ("C:/Users/user/Downloads/reef_fish.txt",header = TRUE,sep="\t", dec=".")# long version
fish<-read.table("C:/Users/user/Downloads/reef_fish.txt", TRUE, "\t",".")# short version
```

You can also use `file.choose()' to locate directly the file on computer

```{r,  eval=FALSE,  tidy=TRUE}
fish<-read.table(file.choose (), header = TRUE,sep="\t", dec=".")
```


```



```{r,  eval=T}
# import data set and create an object in R studio + simple plot 
fish<-read.table('C:/Users/user/Downloads/reef_fish.txt', header=T, sep='\t', dec='.')
barplot(fish$richness, main="Top 10 reef fish Richness (Allen, 2000)", horiz=TRUE, names.arg=fish$country, cex.names=0.5, las=1)
```

**Note 1**: using the options in R studio, you can easily export the resulting plot as and image, a pdf, or to copy it to your clipboard.  
**Note 2**: you can do many many many things using RStudio, and we will just visit the tip of the iceberg together. 


## Git
install.packages('usethis')
library('usethis')
use_git_config(user.name='kuanchun',user.email='kuanchun2001@gmail.com')
use_git()


## GitHub
library('usethis')
create_github_token()
library(gitcreds)
gitcreds_set()
use_github()



<p class="alert">
**`r knitr::asis_output("\U26A0")` Practice 1.3** The goal is to generate an .Rmd and "communicate" with GitHub. Complete **ADVANCED** (see above). In RStudio, try to move both the *.Rmd* and *.html* files to a public repository accessible via your (newly created) Github account. Do not upload the files directly to GitHub, it's useless and remember that you could be picked up for a demo next week. Send the address (URL) of this repository (e.g. https://github.com/vianneydenis/OCEAN5098B.git) to [vianneydenis@g.ntu.edu.tw] **before next Monday** so that your work can be reviewed. If you cannot 'push' your files, you can also send them directly to me as an attachment - but try before giving up. The **title of your email** should be `Practice 1.3 (your name: your student number). It will be a challenge, but once you have completed it, you will have mastered important functionalities of the R environment. Have fun ;)
</p>

</p>

# Credits


> Content derived from Fukami T. & Coyle J. (Standford University) derived itself from Data Carpentry and Software Carpentry materials (Copyright (c) Data Carpentry) under CC-3.0 Attribution License (see http://creativecommons.org/licenses/by/3.0/).